Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-05 GWLDCII.tex
added exposition and abstract, fix parametrized

\section{Introduction}

@@

Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv,Adamo:2012xe,  Boels:2007qn, Bullimore:2010pj}. These integrals are calculated via holomorphic Wilson loops. As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}. Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the space parametrized by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.

In the above work and elsewhere, it is clear that while the space parametrized by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space. For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$. Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, which can be seen by comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}. This is not too alarming, as it is conjectured that the space parametrized by the Wilson loop diagrams will project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.

@@

In Section~\ref{sec dim} we examine the dimension of positroids associated to Wilson loop diagrams, and show that the dimension is always equal to three times the number of propagators in the diagram (Theorem~\ref{thm dim}).  While this has been proved by Marcott in \cite{WLDdim} using matroidal arguments, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram.

@@

In this section we will give an algorithm (Algorithm~\ref{alg:put GN on WLD}) to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid. This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given Wilson loop diagram. Furthemore, we use it to characterize loops and coloops in the positroid associated to a Wilson loop diagram (Corrollary \ref{no coloops}). It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram; indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections.

@@

In continuing to characterise the poistroid cells associated to Wilson loop diagrams, our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$ (Theorem \ref{thm dim}).  The positroid cells associated to the Amplituhedron are of dimension $4|\cP|$. In \cite{non-orientable}, Agarwala and Marcott show that the dimension of the Deodhar component is the sum of $\|\cP\|$ and the dimension fo the associated positroid cell.
%\[|\cP| + \text{ the dimension of associated positroid cell}.\]
\note{What if instead of displaying this we wrote ``is the sum of $\|\cP\|$ and the dimension fo the associated positroid cell.''}\sanote{implemented, but don't like how it no longer stands out. Thoughts?}
In other words, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.

@@

@@

\sanote{Add exposition in this section and in intro about how this allows one to talk about what happens to a postriod cell as one adds a propagator. These results aren't enough, but a starting point, and certainly not done in this paper}

>>>>

\begin{abstract}
  Wilson loop diagrams are an important tool in studying scattering amplitudes of SYM $N=4$ theory and are known by previous work to be associated to positroids. In this paper we study the structure of the associated positroids, as well as the structure of the denominator of integral defined by each diagram. In particular, we give an algorithm to derive the Grassman necklace of the assoicated positroid directly from the Wilson loop diagram. We also give a recursive proof that the dimension of these cells is thrice the number of propagators in the diagram. We also show that the denominator in the integral is the radical of the product of minors defined by the elements of the Grassmann necklace.
\end{abstract}
\section{Introduction}

@@

Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv,Adamo:2012xe,  Boels:2007qn, Bullimore:2010pj}. These integrals are calculated via holomorphic Wilson loops. As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrals associates a volume form to a convex space different from the Amplituhedron \cite{Hodges2013}. Agarwala and Marin-Amat uncovered a connection between the Feynman integrals developed in this literature and positroids, defined  as matroids that can be realized as an element of $\Gr(k,n)$ \cite{wilsonloop}, while other work has shown a connection between the volume filled by Wilson loop diagrams and the Amplituhedron \cite{casestudy, Amplituhedronsquared}.

In the above work and elsewhere, it is clear that while the space filled by the Wilson loop diagrams is related to the Amplituhedron, they are not the same space. For instance, it is conjectured that the Amplituhedron is orientable, whereas Agarwala and Marcott show in \cite{non-orientable} that the space parametrized by the Wilson loop diagrams as a subspace of $\Gr(k, n+1)$ can be seen as a non-orientable vector bundle over some submanifold of $\Gr(k,n)$. Furthermore, the cells associated to the Wilson loop diagrams are different from the cells associated to BCFW diagrams, which can be seen by comparing the results of \cite{AmplituhedronDecomposition} and \cite{casestudy}. This is not too alarming, as it is conjectured that the space parametrized by the Wilson loop diagrams will project down to something close to the Amplituhedron \cite{wilsonloop, Amplituhedronsquared}.

@@

In Section~\ref{sec dim} we examine the dimension of positroids associated to Wilson loop diagrams, and show that the dimension is always equal to three times the number of propagators in the diagram (Theorem~\ref{thm dim}).  While this has been proved by Marcott in \cite{WLDdim} using matroidal arguments, our proof is constructive and explicitly relates the position of the plusses in the Le diagram to the propagators in the Wilson loop diagram. {\color{violet} This proof and the methods used therein are a first step towards understanding how the positroid cell assocaited to a Wilson loop diagram changes as one adds propagators in certain positions.}

@@

In this section we will give an algorithm (Algorithm~\ref{alg:put GN on WLD}) to go directly from a Wilson loop diagram to the Grassmann necklace of its positroid. This is a useful result in and of itself, as it greatly simplifies the process of identifying the positroid associated to a given Wilson loop diagram. Furthemore, we use it to characterize loops and coloops in the positroid associated to a Wilson loop diagram (Corrollary \ref{no coloops}). \hlfix{It also allows us to examine how the positroid changes as we make minor changes to the Wilson loop diagram;}{what does this mean?} {\color{violet} It allows us to see how the Le diagram assoicated to a Wilson loop diagram changes as one adds propagators in certain positions (Theorem \ref{thm dim}).} Indeed, the techniques we develop in this section to verify that our algorithm produces the correct Grassmann necklace will also be used repeatedly in later sections {\color{violet} to calculate the dimension of the associated positroid cell (section \ref{sec dim}) and to study the structure of the poles of the associated integral $I(W)$ (section \ref{sec poles}).}

@@

In continuing to characterise the poistroid cells associated to Wilson loop diagrams, our next goal is to show that the dimension of the positroid cell defined by a Wilson loop diagram $(\cP, [n])$ has dimension $3|\cP|$ (Theorem \ref{thm dim}).  The positroid cells associated to the Amplituhedron are of dimension $4|\cP|$. In \cite{non-orientable}, Agarwala and Marcott show that the dimension of the Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
%\[|\cP| + \text{ the dimension of associated positroid cell}.\]
\note{What if instead of displaying this we wrote ``is the sum of $\|\cP\|$ and the dimension fo the associated positroid cell.''}\sanote{implemented, but don't like how it no longer stands out. Thoughts?}
In other words, the Deodhar component associated to a Wilson loop diagram is $4|\cP|$, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron.

@@

{\color{violet}More than just a dimensionality result, the lemmas below are a first step towards undertanding how the adding an extra propagator changes the associated positroid cell. }

@@
